Mechanising a linear \picalc

### 2020-04-28 paper/paper.tex
Draft swapping

\begin{nitheorem}
  \label{thm:swapping}
  If $\types{\gamma}{\Gamma}{P}{\Xi}$ then $\types{swap_i \; \gamma}{swap_i \; \Gamma}{swap_i \; P}{swap_i \; \Xi}$.
\end{nitheorem}

\todo{}

>>>>

Swapping two variables (in the typing context, input and output usage contexts and process) preserves the well-typedness of a process.

\begin{remark}
  We limit ourselves to the swapping of contiguous variables $i$ and $\suc i$.
  Doing so is enough to prove subject reduction.
  The swapping of any two variables can be modeled as a sequence of contiguous variable swappings.
\end{remark}

\begin{nitheorem}
  \label{thm:swapping}
  Let $swap_i$ be a function that swaps variables $i$ and $\suc i$.
  For simplicity, we overload $swap$ and use it to swap types in a typing context, multiplicities in a usage context, and variable references in a process.
  Let $P$ be a well-typed process such that $\types{\gamma}{\Gamma}{P}{\Xi}$.
  Then $\types{swap_i \; \gamma}{swap_i \; \Gamma}{swap_i \; P}{swap_i \; \Xi}$.
\end{nitheorem}
\begin{proof}
  By induction on \textsc{Process} and \textsc{Var}.
\end{proof}
